\ \\ \LARGE\bf Speculative Evaluation in Particle Swarm Optimization \thanks{Matthew Gardner, Andrew McNabb, and Kevin Seppi are with the Department of Computer Science, Brigham Young University, 3361 TMCB, Provo, UT 84602 (phone: 801-422-8717; email: \{mjg82,a,k\}@cs.byu.edu).}

### 2010-04-21 honors_thesis/journal_paper/paper.tex
Fixed a few problems in the equations

We present results for five common benchmark problems: Rastrigin, Sphere,
Schwefel 2.21, Griewank, and Bohachevsky.  Rastrigin is defined as:
\[f(\Vec{x}) = \sum_{i=1}^D\left(z_i^2 - 10\cos\left(2\pi z_i\right) +
10\right), z=x-c\]
initialized in $[-5.12,5.12]^D$.
Sphere is defined as:
\[f(\Vec{x}) = \sum_{i=1}^D z_i^2, z=x-c\]
initialized in $[-50,50]^D$.
Schwefel 2.21 is defined as:
\[f(\Vec{x}) = \max_i{|z_i|, 1 \leq i \leq D}, z=x-c\]
initialized in $[-500,500]^D$.
Griewank is defined as:
\[f(\Vec{x}) = \frac{1}{4000}\sum_{i=1}^D z_i^2 - \Pi_{i=1}^D
\cos\left(\frac{z_i}{\sqrt{i}} \right) + 1, z=x-c\]
initialized in $[-600,600]^D$
And Bohachevsky is defined as:
\[f(\Vec{x}) = \sum_{i=1}^D(x_i^2+2x_{i+1}^2-.3\cos(3\pi x_i)-.4\cos(4\pi
x_{i+1})+.7)\]
initialized in $[-15,15]^D$.

>>>>

We present results for five common benchmark problems: Rastrigin, Sphere,
Schwefel 2.21, Griewank, and Bohachevsky.

Rastrigin is initialized in $[-5.12,5.12]^D$ and defined as:
\[f(\Vec{x}) = \sum_{i=1}^D\left(z_i^2 - 10\cos\left(2\pi z_i\right) +
10\right), z=x-c\]

Sphere is initialized in $[-50,50]^D$ and defined as:
\[f(\Vec{x}) = \sum_{i=1}^D z_i^2, z=x-c\]

Schwefel 2.21 is initialized in $[-500,500]^D$ and defined as:
\[f(\Vec{x}) = \max_i{|z_i|, 1 \leq i \leq D}, z=x-c\]

Griewank is initialized in $[-600,600]^D$ and defined as:
\[f(\Vec{x}) = \frac{1}{4000}\sum_{i=1}^D z_i^2 - \Pi_{i=1}^D
\cos\left(\frac{z_i}{\sqrt{i}} \right) + 1, z=x-c\]

And Bohachevsky is initialized in $[-15,15]^D$ and defined as:
\[f(\Vec{x}) = \sum_{i=1}^D(x_i^2+2x_{i+1}^2-.3\cos(3\pi x_i)-.4\cos(4\pi
x_{i+1})+.7)\]
